---
title: "Abacavirinol"
author: "Christian Celis"
date: "December 5, 2018"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
```
```{r}
LBGTguys <- filter(abac, LBGT=="yes")
men <- filter(abac, sex=="M")
women <- filter(abac, sex=="F")
DrugUser <- filter(abac, Ivdrug=="user")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

We have been given a new drug named abacavirinol which is under trial and we will analyze the effectiveness of this drug by giving the drug to all people, drugUser, LBGTguys, men, and women. To analyze this dat we will be using a barchart, table, chitest, and fisher test to compare the differnces in the results.

# Everyone Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment  , data=abac, type = "percent")  
```

In this barchart, we are comparing all people who have been given abacavirinol to people who have been given a placebo and comparing if these individuals got aids or if the drug they have been given is really working. After carefully comparing the two it seems as if the drug is working because out of all the people who took the drug it seems that only about 40% of them got AIDS and almost 60% of the people who took the placebo got aids

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1=xtabs(~treatment + infected  , data=abac)
rowPerc(table1)
colPerc(table1)
```

In this table we will be comparing and analyzing whether or not if the new drug abacavirinol will work when given to a group a people compared to a group of people who have been given a placebo. after carefully reviewing the results that the table has given we have noticed that out of the people who recieved the drug only about 40.93% of them got aids compared to the 59.07% of people who got aids who recieved the placebo.     

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

$H_0$ Considering that the p value is below 0.5 we will reject the null hypothesis  
$H_a$ consdiering the p value is below 0.5 we will accept the alternative   

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

After carefully reviewing the results we have came to the conclusion that when giving the drug abacavirinol to these group of people, it gives us results that it is working. 

#LGBTguysResults

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment  , data=LBGTguys, type = "percent")  
```
In this barchart, we are comparing LGBTguys who have been given abacavirinol to a group of LBGTguys who have been given a placebo and comparing if these individuals got aids or if the drug they have been given is really working. After carefully comparing the two it seems as if the drug is not working because out of all guys who took the drug it seems that more than 60% of them got AIDS and less then half of the guys who who took the placebo got aids

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table2=xtabs(~treatment + infected  , data=LBGTguys)
rowPerc(table2)
colPerc(table2)
```

In this table we will be comparing and analyzing whether or not if the new drug abacavirinol will work when given to LGBTguys compared to a group LGBTguys who have been given a placebo. after carefully reviewing the results that the table has given we have noticed that out of the guys who recieved the drug about 68.97%% of them got aids compared to the 31.03% of people who got aids who recieved the placebo. The results clearly show that the drug is not working for this group of people.   

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table2)
chisqtestGC(table2)
fisher.test(table2)
```

$H_0$ Considering that the p value is below 0.5 we will reject the null hypothesis  
$H_a$ consdiering the p value is below 0.5 we will accept the alternative   

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

 After carefully reviewing the results we have came to the conclusion that when giving the drug abacavirinol to these group of people, it gives us results that it is not working. 
 
#Men Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment  , data=men, type = "percent")  
```
In this barchart, we are comparing men who have been given abacavirinol to a group of men who have been given a placebo and comparing if these individuals got aids or if the drug they have been given is really working. After carefully comparing the two it seems as if the drug is not working and it working backwards. more than 60% of the men who received the placebo got aids and about 30% of the men who receievd the drug got aids. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table3=xtabs(~treatment + infected  , data=men)
rowPerc(table3)
colPerc(table3)
```

In this table we will be comparing and analyzing whether or not if the new drug abacavirinol will work when given to men compared to a group LGBTguys who have been given a placebo. after carefully reviewing the results that the table has given we have noticed that out of the guys who recieved the drug about 30.46% of them got aids compared to the 69.54% of men who got aids who recieved the placebo. The results clearly show that the drug is not working for this group of people and it is working backwards. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table3)
chisqtestGC(table3)
fisher.test(table3)
```

$H_0$  Considering that the p value is below 0.5 we will reject the null hypothesis  
$H_a$  consdiering the p value is below 0.5 we will accept the alternative   


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

After carefully reviewing the results we have came to the conclusion that when giving the drug abacavirinol to these group of people, it gives us results that it is not working and it is working backwards.


#Women Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment  , data=women, type = "percent")  
```
In this barchart, we are comparing women who have been given abacavirinol to a group of women who have been given a placebo and comparing if these individuals got aids or if the drug they have been given is really working. After carefully comparing the two it seems as if the drug is not working and it working backwards. more than 60% of the women who received the drug got aids and about 50% of the women who receievd the placebo got aids.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table4=xtabs(~treatment + infected  , data=women)
rowPerc(table4)
colPerc(table4)
```
In this table we will be comparing and analyzing whether or not if the new drug abacavirinol will work when given to women compared to a group women who have been given a placebo. after carefully reviewing the results that the table has given we have noticed that out of the guys who recieved the placebo about 40.7% of them got aids compared to the 59.3% of women who got aids who recieved the drug. The results clearly show that the drug is not working for this group of people.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table4)
chisqtestGC(table4)
fisher.test(table4)
```
$H_0$ Considering that the p value is below 0.5 we will reject the null hypothesis  
$H_a$ consdiering the p value is below 0.5 we will accept the alternative   


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

After carefully reviewing the results we have came to the conclusion that when giving the drug abacavirinol to these group of people, it gives us results that it is not working.

#Drug User Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~infected + treatment  , data=DrugUser, type = "percent")  
```

In this barchart, we are comparing drug users who have been given abacavirinol to a group of drug users who have been given a placebo and comparing if these individuals got aids or if the drug they have been given is really working. After carefully comparing the two it seems as if the drug is working. more than 30% of the drug users who received the drug got aids and more than 50% of the drug users who receievd the placebo got aids.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table5=xtabs(~treatment + infected  , data=DrugUser)
rowPerc(table5)
colPerc(table5)
```
In this table we will be comparing and analyzing whether or not if the new drug abacavirinol will work when given to drug users compared to a group drug users who have been given a placebo. after carefully reviewing the results that the table has given we have noticed that out of the drug users who recieved the placebo about 74.36% of them got aids compared to the 25.64% of the drug users who got aids who recieved the drug. The results clearly show that the drug is working for this group of people.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table5)
chisqtestGC(table5)
fisher.test(table5)
```

$H_0$ Considering that the p value is below 0.5 we will reject the null hypothesis  
$H_a$ consdiering the p value is below 0.5 we will accept the alternative   

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

After carefully reviewing the results we have came to the conclusion that when giving the drug abacavirinol to these group of people, it gives us results that it is working.
